---
title: "Part 06 - Reporting with Quarto"
subtitle: "Introduction to R for Health Data Science: Hands-on training"
author: "Carlos Matos"
format: html
number-sections: false
toc: true
bibliography: references.bib
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/american-medical-association.csl"
---

# Exploring the gapminder dataset

This document is part of the Introduction to R for Health Data Science: Hands-on training.

We will take a closer look at Portugal. \
In @sec-portugal-over-time we will look at how life expectancy changed in Portugal over time.\
In @sec-portugal-reg we will make a regression of lifeExp over gdpPercap in Portugal and report the results.

First, let's load the necessary packages: [@tidyverse; @gapminder; @report; @Gizaw2019]

```{r}
#| echo: fenced
#| message: false
#| warning: false
library(tidyverse)
library(gapminder)
library(report)
```

Then, let's take a look at the dataset.

```{r}
gapminder %>% glimpse()
```

We see a tibble with `r nrow(gapminder)` rows and `r length(gapminder)` columns.

## Portugal analysis

### Over time {#sec-portugal-over-time}

```{r}
gapminder %>% 
  filter(country == "Portugal") %>% 
  ggplot(aes(x = year, y = lifeExp)) +
  geom_line(color = "darkred") +
  geom_point(color = "darkgreen")
```

We see that that life expectancy **increased continuously.**

### Regression modelling {#sec-portugal-reg}

```{r}
gapminder_pt <- gapminder %>% 
  filter(country == "Portugal")

lm(lifeExp ~ gdpPercap, data = gapminder_pt) %>% 
  report()
```

# References

::: {#refs}
:::

# ANNEX
